Austria's Covid legislation: Duration of parliamentarian consultation period in comparision.

### 2021-02-22 _post/2019-11-20-vorzugsstimmen/vorzugsstimmen.Rmd
modified post.json

```{r echo=FALSE, message=FALSE, warning=TRUE}
df_merge %>% 
  reactable(.,
          filterable = T,
          pagination = T,
          height = 250,
          outlined = T,
          bordered = F,
          compact=T,
          theme=reactableTheme(backgroundColor = plot_bg_color,
                           style=list(fontFamily="Karla",
                                      fontSize="12px"),
                           filterInputStyle = list(
                             color="black",
                             backgroundColor = plot_bg_color)))

@@

```{r message=FALSE, warning=FALSE, paged.print=TRUE, code_folding=NULL, echo=F}
library(reactable)
n_mandates_regional_districts %>% 
  reactable(.,
            filterable = T,
          pagination = T,
          height = 250,
          outlined = T,
          bordered = F,
          compact=T,
          theme=reactableTheme(backgroundColor = plot_bg_color,
                           style=list(fontFamily="Karla",
                                      fontSize="12px"),
                           filterInputStyle = list(
                             color="black",
                             backgroundColor = plot_bg_color)))

>>>>

```{r echo=FALSE, message=FALSE, warning=TRUE, eval=F}
#table.start
df_merge %>% 
  reactable(.,
          filterable = T,
          pagination = T,
          height = 250,
          outlined = T,
          bordered = F,
          compact=T,
          theme=reactableTheme(backgroundColor = plot_bg_color,
                           style=list(fontFamily="Karla",
                                      fontSize="12px"),
                           filterInputStyle = list(
                             color="black",
                             backgroundColor = plot_bg_color)))
#table.end
```

@@

```{r message=FALSE, warning=FALSE, paged.print=TRUE, code_folding=NULL, echo=F, eval=F}
#table.start
library(reactable)
n_mandates_regional_districts %>% 
  reactable(.,
            filterable = T,
          pagination = T,
          height = 250,
          outlined = T,
          bordered = F,
          compact=T,
          theme=reactableTheme(backgroundColor = plot_bg_color,
                           style=list(fontFamily="Karla",
                                      fontSize="12px"),
                           filterInputStyle = list(
                             color="black",
                             backgroundColor = plot_bg_color)))

#table.end
```

### 2021-02-22 _post/2020-06-08-update-on-mobility-patterns/update-on-mobility-patterns.Rmd
modified post.json

```{r include=FALSE}
options(noaakey = Sys.getenv("noaakey"))
```
<details closed> 
<summary>Get weather data, merge datasets</summary>
```{r eval=TRUE, fig.height=6}
library(rnoaa)
#get all stations in Austria
df_AT <- ncdc_stations(locationid='FIPS:AU')$data

@@

#get temperature data
df_res <- ncdc(datasetid = "GHCND", stationid = df_stations$id, datatypeid = "TAVG", startdate = "2020-01-01", enddate = "2020-06-01",
     add_units=T, limit=1000)

>>>>

```{r include=FALSE}
options(noaakey = Sys.getenv("noaakey"))
```
<details closed> 
<summary>Get weather data, merge datasets</summary>
```{r eval=TRUE, fig.height=6}
library(rnoaa)
#get all stations in Austria
df_AT <- ncdc_stations(locationid='FIPS:AU', token=Sys.getenv("noaakey"))$data

@@

#get temperature data
df_res <- ncdc(datasetid = "GHCND", 
               stationid = df_stations$id, 
               datatypeid = "TAVG", 
               startdate = "2020-01-01", 
               enddate = "2020-06-01", 
               token=Sys.getenv("noaakey"),
               add_units=T, 
               limit=1000)

### 2021-02-22 _post/2020-07-21-attransperency/attransperency.Rmd
modified post.json

```{r echo=TRUE, fig.height=7}
df_position_labels <- df_position_long %>% 
  filter(!position %in% c("executive_non_remunerated_n",
                        "total_n")) %>% 
  group_by(party, position) %>% 
  mutate(party=fct_infreq(party)) %>% 
  summarise(label_median=median(number),
            label_mean=mean(number),
            label_max=max(number),
            label_min=min(number))

@@

```{r echo=FALSE}
pl_box
```

>>>>

```{r echo=TRUE, fig.height=7, code_folding=F}
df_position_labels <- df_position_long %>% 
  filter(!position %in% c("executive_non_remunerated_n",
                        "total_n")) %>% 
  group_by(party, position) %>% 
  mutate(party=fct_infreq(party)) %>% 
  summarise(label_median=median(number),
            label_mean=mean(number),
            label_max=max(number),
            label_min=min(number))

@@

```{r echo=FALSE, fig.height=7, fig.width=10, code_folding=NULL}
pl_box
```

### 2021-02-22 _post/2020-10-10-vienna-elections-2020-age-profile/vienna-elections-2020-age-profile.Rmd
modified post.json

---
title: "Vienna Elections 2020: Age profile of electoral candidates"
description: |
  A short description of the post.
date: 10-10-2020

@@

![](/post/2020-10-10-vienna-elections-2020-age-profile_files/Inkedtext_flow_LI_Moment.jpg){width=50% height=50%}

@@

```{r echo=FALSE}
html_tb_all
```

@@

```
</details>
```{r echo=FALSE}
html_tb_young
```

@@

```{r echo=FALSE}
html_tb_old

@@

### Graph
<br>
Hover with the mouse over the box plot and dots to obtain the pertaining data.
<details closed> 
<summary>Code: graph</summary> 
```{r}
df_age_list_district_graph <- df_clean %>% 
  filter(!str_detect(election, "Stadt")) %>% 
  group_by(election, wahlkreis, party) %>% 
  mutate(year_median=median(year_birth, na.rm=T),
    year_mean=mean(year_birth, na.rm=T),
    year_se=sd(year_birth, na.rm=T),
    values_nested=list(year_birth=year_birth)) %>% 
  group_by(election) %>% 
  mutate(median_election=median(year_birth, na.rm = T)) %>% 
  group_by(election, wahlkreis) %>% 
  mutate(median_wahlkreis=median(year_birth, na.rm=T)) %>% 
  ungroup() %>% 
  mutate(wahlkreis_num=str_extract(wahlkreis, regex("\\d+")) %>% as.numeric()) %>% 
  mutate(wahlkreis_fac=fct_reorder(wahlkreis, wahlkreis_num)) %>% 
  mutate(party=fct_rev(party))

@@

```
</details>
```{r echo=FALSE}
html_age_list_district
```
<br>

@@

```{r echo=FALSE}
tb_residence_party
```

@@

```{r echo=FALSE}
tb_residence_district
```
<br>

>>>>

---
title: "Vienna Elections 2020: Age profile of electoral candidates"
description: |
  An empirical look at candidates' age.
date: 10-10-2020

@@

![](vienna-elections-2020-age-profile_files/Inkedtext_flow_LI_Moment.jpg){width=50% height=50%}

@@

```{r echo=FALSE}
#table.start
html_tb_all
#table.end
```

@@

```
</details>
```{r echo=FALSE}
#table.start
html_tb_young
#table.end
```

@@

```{r echo=FALSE}
#table.start
html_tb_old
#table.end
```
<br>

@@

### Graph
<br>

Hover with the mouse over the box plot and dots to obtain the pertaining data.

<details closed> 
<summary>Code: graph</summary> 
```{r}
df_age_list_district_graph <- df_clean %>% 
  filter(!str_detect(election, "Stadt")) %>% 
  group_by(election, wahlkreis, party) %>% 
  mutate(year_median=median(year_birth, na.rm=T),
    year_mean=mean(year_birth, na.rm=T),
    year_se=sd(year_birth, na.rm=T),
    values_nested=list(year_birth=year_birth)) %>% 
  group_by(election) %>% 
  mutate(median_election=median(year_birth, na.rm = T)) %>% 
  group_by(election, wahlkreis) %>% 
  mutate(median_wahlkreis=median(year_birth, na.rm=T)) %>% 
  ungroup() %>% 
  mutate(wahlkreis_num=str_extract(wahlkreis, regex("\\d+")) %>% as.numeric()) %>% 
  mutate(wahlkreis_fac=fct_reorder(wahlkreis, wahlkreis_num)) %>% 
  mutate(party=fct_rev(party))

@@

```
</details>
```{r echo=FALSE}
#table.start
html_age_list_district
#table.end
```
<br>

@@

```{r echo=FALSE}
#table.start
tb_residence_party
#table.end
```

@@

```{r echo=FALSE}
#table.start
tb_residence_district
#table.end
```
<br>

### 2021-02-22 _post/2020-12-19-vienna-elections-2020-analysis-of-parties-ads-on-facebook/welcome.Rmd
css backgroud white
modified post.json

fpoe <- "#005DA8"
neos <- "#EA5290"
oevp <- "#5DC2CC"
spoe <- "#FC0204"
greens <- "#A3C630"
strache <- "White"
bier <- "yellow"

@@

fn_reactable_headings(title="WIEN-WAHL 2020: Facebook pages within scope and affiliated party", subtitle="", body = rt_pages, caption=my_caption)

@@

fn_reactable_headings(title="WIEN-WAHL 2020: All Facebook ads",
                      subtitle=glue::glue("Ads posted between {date_observation_start_format} and {date_observation_end_format}"),
                      body = tb_all,
                      caption=my_caption)
```

@@

```{r echo=FALSE}
fn_reactable_headings(title="WIEN-WAHL 2020: Number and total amount spent by party",
                      subtitle=glue::glue("Click to see details for indiviudal Facebook pages. Ads placed between {date_observation_start_format} and {date_observation_end_format}."),
                      body=rt_party_pages,
                      caption=my_caption)

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
fn_reactable_headings(title="Impressions",
                      subtitle="",
                      body = rt_impressions,
                      caption = my_caption)
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
fn_reactable_headings(title="WIEN-WAHL 2020: Accounts which placed ads with a median female audience share of >50%", subtitle="", body = rt_female, caption=my_caption)

```
<br>
Indeed, as the table above shows there were indeed a few pages with an average female audience share larger than 50 %. What is noteworthy, these pages belong almost exclusively to the Greens. There were only `r df_female %>% filter(party=="SPÖ") %>% nrow()` pages which belonged to the SPÖ, and `r df_female %>% filter(party=="ÖVP") %>% nrow()` to the ÖVP. There was not a single page from the FPÖ, Strache and, more surprisingly, the Neos.

>>>>

fpoe <- "#005DA8"
neos <- "#EA5290"
oevp <- "#5DC2CC"
spoe <- "#FC0204"
greens <- "#A3C630"
strache <- "grey50"
bier <- "yellow"

@@

#table.start
fn_reactable_headings(title="WIEN-WAHL 2020: Facebook pages within scope and affiliated party", subtitle="", body = rt_pages, caption=my_caption)
#table.end

@@

#table.start
fn_reactable_headings(title="WIEN-WAHL 2020: All Facebook ads",
                      subtitle=glue::glue("Ads posted between {date_observation_start_format} and {date_observation_end_format}"),
                      body = tb_all,
                      caption=my_caption)
#table.end
```

@@

```{r echo=FALSE}
#table.start
fn_reactable_headings(title="WIEN-WAHL 2020: Number and total amount spent by party",
                      subtitle=glue::glue("Click to see details for indiviudal Facebook pages. Ads placed between {date_observation_start_format} and {date_observation_end_format}."),
                      body=rt_party_pages,
                      caption=my_caption)
#table.end
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
#table.start
fn_reactable_headings(title="Impressions",
                      subtitle="",
                      body = rt_impressions,
                      caption = my_caption)
#table.end
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
#table.start
fn_reactable_headings(title="WIEN-WAHL 2020: Accounts which placed ads with a median female audience share of >50%", subtitle="", body = rt_female, caption=my_caption)
#table.end
```
<br>
Indeed, as the table above shows there were indeed a few pages with an average female audience share larger than 50 %. What is noteworthy, these pages belong almost exclusively to the Greens. There were only `r df_female %>% filter(party=="SPÖ") %>% nrow()` pages which belonged to the SPÖ, and `r df_female %>% filter(party=="ÖVP") %>% nrow()` to the ÖVP. There was not a single page from the FPÖ, Strache and, more surprisingly, the Neos.

### 2021-02-22 _post/2020-12-22-submissionsepidemiclaw/submissionsepidemiclaw.Rmd
modified post.json

```{r echo=FALSE, paged.print=TRUE}
reactable(df_submission, 
          defaultPageSize = 4, 
          columns = list(
            link_single_submission_page = colDef(
              cell = function(value) {
                url <- value
                htmltools::tags$a(href = url, 
                                  target = "_blank", 
                                  value)
                },
              width = 150,
              html=TRUE
              )),
          filterable = TRUE,
          bordered=TRUE,
          compact = TRUE,
          style = list(fontSize = "10px"),
          theme = reactableTheme(
            backgroundColor = plot_bg_color,
                filterInputStyle = list(
                  color="green",
                  backgroundColor = plot_bg_color)))
```

@@

```{r echo=FALSE}
tb_text
```

@@

```{r echo=FALSE}
reactable(df_collocs,
          bordered=TRUE,
          compact = TRUE,
          style = list(fontSize = "10px"),
          filterable = TRUE,
          theme = reactableTheme(
            backgroundColor = plot_bg_color,
                filterInputStyle = list(
                  color="green",
                  backgroundColor = plot_bg_color)))
```

@@

```{r echo=FALSE}
reactable(head(df_similarity, n = 10^3),
          columns=list(
            cosine=colDef(format=colFormat(digits=4),
                          align="left")),
          bordered=TRUE,
          compact = TRUE,
          style = list(fontSize = "10px"),
          filterable = TRUE,
          theme = reactableTheme(
            backgroundColor = plot_bg_color,
                filterInputStyle = list(
                  color="green",
                  backgroundColor = plot_bg_color)))

>>>>

```{r echo=FALSE, paged.print=TRUE}
#table.start
reactable(df_submission, 
          defaultPageSize = 4, 
          columns = list(
            link_single_submission_page = colDef(
              cell = function(value) {
                url <- value
                htmltools::tags$a(href = url, 
                                  target = "_blank", 
                                  value)
                },
              width = 150,
              html=TRUE
              )),
          filterable = TRUE,
          bordered=TRUE,
          compact = TRUE,
          style = list(fontSize = "10px"),
          theme = reactableTheme(
            backgroundColor = plot_bg_color,
                filterInputStyle = list(
                  color="green",
                  backgroundColor = plot_bg_color)))
#table.end
```

@@

```{r echo=FALSE}
#table.start
tb_text
#table.end
```

@@

```{r echo=FALSE}
#table.start
reactable(df_collocs,
          bordered=TRUE,
          compact = TRUE,
          style = list(fontSize = "10px"),
          filterable = TRUE,
          theme = reactableTheme(
            backgroundColor = plot_bg_color,
                filterInputStyle = list(
                  color="green",
                  backgroundColor = plot_bg_color)))
#table.end
```

@@

```{r echo=FALSE}
#table.start
reactable(head(df_similarity, n = 10^3),
          columns=list(
            cosine=colDef(format=colFormat(digits=4),
                          align="left")),
          bordered=TRUE,
          compact = TRUE,
          style = list(fontSize = "10px"),
          filterable = TRUE,
          theme = reactableTheme(
            backgroundColor = plot_bg_color,
                filterInputStyle = list(
                  color="green",
                  backgroundColor = plot_bg_color)))
#table.end

### 2021-02-22 _post/2021-01-22-covidconsultationduration/covidconsultationduration.Rmd
modified post.json

```{r chunk_duration_legis_period, echo=F, code_folding=NULL, include=F}
pl_duration_legis_period<- df_consolidated %>%
  filter(duration_collected>=0) %>% 
  mutate(legis_period_fac=as.roman(legis_period) %>% as.integer %>% as.character() %>%  fct_inseq()) %>% 
  ungroup() %>% 
  ggplot()+
  labs(title="Distribution of length of consultative periods.",
       subtitle="",
       x="legislative period",
       y="duration in days",
       caption=caption) +
  geom_violin(aes(x=legis_period_fac,
                  y=duration_collected),
              fill="grey50",
              color="grey50"
              )+
  geom_hline(yintercept=6*7,
             linetype="dotted",
             color="grey50")+
  geom_text(label="requested six\nweek duration\n(42 days)",
            y=6*7+5,
            x=length(unique(df_consolidated$legis_period))+1,
            color="grey50",
            vjust=0,
            hjust=0,
            size=3,
            lineheight=0.7,
            family="Roboto Condensed",
            check_overlap = T)+
  geom_point_interactive(data=. %>% 
                           group_by(legis_period_fac) %>% summarise(duration_collected_median=median(duration_collected, na.rm = T)),
                         aes(
                           x=legis_period_fac,
                           y=duration_collected_median,
                           group=legis_period_fac,
                           tooltip=glue::glue("Median duration of consultative period: {duration_collected_median}")
                         ),
                         color="firebrick")+
  scale_color_manual(label=c("firebrick"="median length of consultative period"),
                     values=c("firebrick"="firebrick"))+
  scale_x_discrete(labels = function(x) as.roman(x),
                   expand=expansion(mult=c(0.05,.3)))+
  scale_y_continuous(breaks=c(seq(0, 400, 100), 42))+
  coord_cartesian(ylim=c(0, 400))+  #set limits here and not in scale_y to zoom in
  theme_post()+
  theme(plot.title.position = "panel",
        legend.position = "top",
        legend.direction = "horizontal",
        legend.justification = "left",
        legend.title = element_blank(),
        axis.title.x = element_text(hjust=0,
                                    color="grey50"),
        axis.title.y=element_text(hjust=0, 
                                  color="grey50",
                                  angle=90))

@@

```{r ref.label="chunk_reactable", code_folding=NULL, eval=F, echo=F}

```{r, layout="l-body-outset", code_folding=NULL, echo=F}
tb_consolidated
```

@@

```{r code_folding=NULL, include=T, echo=F, layout="l-body-outset"}
df_consolidated %>% 
  filter(duration_collected>=0) %>% 
  filter(bill_id=="ME_00294") %>% 
  filter(legis_period=="XXIV") %>% 
  mutate(link_submissions=paste0(link_single_bill_page, "#tab-Stellungnahmen")) %>% 
  select(legis_period, 
         title, 
         bill_id, 
         pdf_pages_sum, 
         date_start_min, 
         date_end_max, 
         duration_collected, 
         n_obs_submissions, 
         link_single_bill_page,
         link_submissions) %>%   
  reactable(.,
              columns=list(
              legis_period=colDef(name="legilsative period",
                                  width=70),
              title=colDef(name="bill's name",
                           minWidth=160),
              bill_id=colDef(name="bill id", 
                             align="right",
                             minWidth=50),
              pdf_pages_sum=colDef(name="# pages total",
                                   minWidth=50),
              date_start_min=colDef(show=F,
                                    name="start",
                                    align="right",
                                    ),
              date_end_max=colDef(show=F, 
                                  name="end",
                                  align="right"),
              duration_collected=colDef(name="duration",
                                        align="right",
                                        minWidth=50),
              n_obs_submissions=colDef(name="# submissions",
                                       minWidth=70),
              link_single_bill_page=colDef(
                name="link bill",
                show=T,
                filterable = F,
                width=50, 
                align="right",
                cell=function(value){
                  htmltools::tags$a(href=value,
                                    target="_blank",
                                    "Link")}),
              link_submissions=colDef(name="link submissions",
                                     show=T,
                                     filterable = F,
                                     width=100,
                                     align="right",
                                     cell = function(value) {
                                       htmltools::tags$a(href=value, target = "_blank", paste0("Link"))})),
            defaultSorted = list(n_obs_submissions = "desc"),
            sortable = T,
            compact = T,
            filterable = T,
            outlined = TRUE,
            theme=rt_theme,
            details=function(index) {
              df_consolidated_pos <- df_consolidated %>%
                filter(duration_collected>=0) %>%
                filter(bill_id=="ME_00294") %>% 
                filter(legis_period=="XXIV") 
              df_duration_details <- df_duration[df_duration$link_single_bill_page == df_consolidated_pos$link_single_bill_page[index],]
                df_duration_details %>% 
                select(starts_with("date")) %>% 
                reactable(., 
                          columns = list(
                            date_start=colDef(show=T, 
                                              name="consultation start"),
                            date_end=colDef(show=T,
                                            name="consultation end")),
                          fullWidth = F,
                          theme=reactableTheme(style=list(
                            margin="0px 0px 0px 50px",
                            backgroundColor=plot_bg_color)))
              })
```

@@

df_dates_missing %>% 
  select(legis_period, title, bill_id, contains("date"), link_single_bill_page) %>% 
  reactable(.,
            columns=list(
               legis_period=colDef(name="legilsative period",
                                  width=70),
              title=colDef(name="bill's name",
                           minWidth=160),
              bill_id=colDef(name="bill id", 
                             align="right",
                             minWidth=50),
              link_single_bill_page=colDef(
                name="link bill",
                show=T,
                filterable = F,
                width=50, 
                align="right",
                cell=function(value){
                  htmltools::tags$a(href=value,
                                    target="_blank",
                                    "Link")})),
            theme=rt_theme)

@@

```{r, eval=T, code_folding=NULL, include=T, layout="l-body-outset"}
df_duration_collected %>% 
  filter(duration_collected<0) %>% 
  mutate(duration_collected=as.numeric(duration_collected)) %>% 
  select(legis_period, title, bill_id, contains("date_"), duration_collected, link_single_bill_page) %>% 
  reactable(.,
            columns=list(
              legis_period=colDef(name="legilsative period",
                                  width=70),
              title=colDef(name="bill's name",
                           minWidth=160),
              bill_id=colDef(name="bill id", 
                             align="right",
                             minWidth=50),
              duration_collected=colDef(name="duration",
                                        format = colFormat(digits = 0)),
              link_single_bill_page=colDef(
                name="link bill",
                show=T,
                filterable = F,
                width=50, 
                align="right",
                cell=function(value){
                  htmltools::tags$a(href=value,
                                    target="_blank",
                                    "Link")})),
            theme=rt_theme)
```

>>>>

```{r chunk_duration_legis_period, echo=F, code_folding=NULL, include=F}
pl_duration_legis_period<- df_consolidated %>%
  filter(duration_collected>=0) %>% 
  mutate(legis_period_fac=as.roman(legis_period) %>% as.integer %>% as.character() %>%  fct_inseq()) %>% 
  ungroup() %>% 
  ggplot()+
  labs(title="Distribution of length of consultative periods.",
       subtitle="Red dot indicates median value.",
       x="legislative period",
       y="duration in days",
       caption=caption) +
  geom_violin(aes(x=legis_period_fac,
                  y=duration_collected),
              fill="grey50",
              color="grey50"
              )+
  geom_hline(yintercept=6*7,
             linetype="dotted",
             color="grey50")+
  geom_text(label="requested six\nweek duration\n(42 days)",
            y=6*7+5,
            x=length(unique(df_consolidated$legis_period))+1,
            color="grey50",
            vjust=0,
            hjust=0,
            size=3,
            lineheight=0.7,
            family="Roboto Condensed",
            check_overlap = T)+
  geom_point_interactive(data=. %>% 
                           group_by(legis_period_fac) %>% summarise(duration_collected_median=median(duration_collected, na.rm = T)),
                         aes(
                           x=legis_period_fac,
                           y=duration_collected_median,
                           group=legis_period_fac,
                           tooltip=glue::glue("Median duration of consultative period: {duration_collected_median}")
                         ),
                         color="firebrick")+
  scale_color_manual(label=c("firebrick"="median length of consultative period"),
                     values=c("firebrick"="firebrick"))+
  scale_x_discrete(labels = function(x) as.roman(x),
                   expand=expansion(mult=c(0.05,.3)))+
  scale_y_continuous(breaks=c(seq(0, 400, 100), 42))+
  coord_cartesian(ylim=c(0, 400))+  #set limits here and not in scale_y to zoom in
  theme_post()+
  theme(plot.title.position = "panel",
        legend.position = "top",
        legend.direction = "horizontal",
        legend.justification = "left",
        legend.title = element_blank(),
        axis.title.x = element_text(hjust=0,
                                    color="grey50"),
        axis.title.y=element_text(hjust=0, 
                                  color="grey50",
                                  angle=90))

@@

```{r, layout="l-body-outset", code_folding=NULL, echo=F}
#table.start
tb_consolidated
#table.end
```

@@

```{r code_folding=NULL, include=T, echo=F, layout="l-body-outset"}
#table.start
df_consolidated %>% 
  filter(duration_collected>=0) %>% 
  filter(bill_id=="ME_00294") %>% 
  filter(legis_period=="XXIV") %>% 
  mutate(link_submissions=paste0(link_single_bill_page, "#tab-Stellungnahmen")) %>% 
  select(legis_period, 
         title, 
         bill_id, 
         pdf_pages_sum, 
         date_start_min, 
         date_end_max, 
         duration_collected, 
         n_obs_submissions, 
         link_single_bill_page,
         link_submissions) %>%   
  reactable(.,
              columns=list(
              legis_period=colDef(name="legilsative period",
                                  width=70),
              title=colDef(name="bill's name",
                           minWidth=160),
              bill_id=colDef(name="bill id", 
                             align="right",
                             minWidth=50),
              pdf_pages_sum=colDef(name="# pages total",
                                   minWidth=50),
              date_start_min=colDef(show=F,
                                    name="start",
                                    align="right",
                                    ),
              date_end_max=colDef(show=F, 
                                  name="end",
                                  align="right"),
              duration_collected=colDef(name="duration",
                                        align="right",
                                        minWidth=50),
              n_obs_submissions=colDef(name="# submissions",
                                       minWidth=70),
              link_single_bill_page=colDef(
                name="link bill",
                show=T,
                filterable = F,
                width=50, 
                align="right",
                cell=function(value){
                  htmltools::tags$a(href=value,
                                    target="_blank",
                                    "Link")}),
              link_submissions=colDef(name="link submissions",
                                     show=T,
                                     filterable = F,
                                     width=100,
                                     align="right",
                                     cell = function(value) {
                                       htmltools::tags$a(href=value, target = "_blank", paste0("Link"))})),
            defaultSorted = list(n_obs_submissions = "desc"),
            sortable = T,
            compact = T,
            filterable = T,
            outlined = TRUE,
            theme=rt_theme,
            details=function(index) {
              df_consolidated_pos <- df_consolidated %>%
                filter(duration_collected>=0) %>%
                filter(bill_id=="ME_00294") %>% 
                filter(legis_period=="XXIV") 
              df_duration_details <- df_duration[df_duration$link_single_bill_page == df_consolidated_pos$link_single_bill_page[index],]
                df_duration_details %>% 
                select(starts_with("date")) %>% 
                reactable(., 
                          columns = list(
                            date_start=colDef(show=T, 
                                              name="consultation start"),
                            date_end=colDef(show=T,
                                            name="consultation end")),
                          fullWidth = F,
                          theme=reactableTheme(style=list(
                            margin="0px 0px 0px 50px",
                            backgroundColor=plot_bg_color)))
              })
#table.end
```

@@

#table.start
df_dates_missing %>% 
  select(legis_period, title, bill_id, contains("date"), link_single_bill_page) %>% 
  reactable(.,
            columns=list(
               legis_period=colDef(name="legilsative period",
                                  width=70),
              title=colDef(name="bill's name",
                           minWidth=160),
              bill_id=colDef(name="bill id", 
                             align="right",
                             minWidth=50),
              link_single_bill_page=colDef(
                name="link bill",
                show=T,
                filterable = F,
                width=50, 
                align="right",
                cell=function(value){
                  htmltools::tags$a(href=value,
                                    target="_blank",
                                    "Link")})),
            theme=rt_theme)
#table.end
```

@@

```{r, eval=T, code_folding=NULL, include=T, layout="l-body-outset"}

#table.start
df_duration_collected %>% 
  filter(duration_collected<0) %>% 
  mutate(duration_collected=as.numeric(duration_collected)) %>% 
  select(legis_period, title, bill_id, contains("date_"), duration_collected, link_single_bill_page) %>% 
  reactable(.,
            columns=list(
              legis_period=colDef(name="legilsative period",
                                  width=70),
              title=colDef(name="bill's name",
                           minWidth=160),
              bill_id=colDef(name="bill id", 
                             align="right",
                             minWidth=50),
              duration_collected=colDef(name="duration",
                                        format = colFormat(digits = 0)),
              link_single_bill_page=colDef(
                name="link bill",
                show=T,
                filterable = F,
                width=50, 
                align="right",
                cell=function(value){
                  htmltools::tags$a(href=value,
                                    target="_blank",
                                    "Link")})),
            theme=rt_theme)
#table.end
```
